\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage{geometry}
 \geometry{
 a4paper,
 margin=0.3in,
 right = 13mm,
 top = 20mm
 }
\usepackage{graphicx}
\usepackage{url}
\usepackage{enumitem}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{hyperref}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\setlength{\marginparsep}{0pt}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\hyphenpenalty=10000
\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.98\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{2.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}

\textbf{Ashutosh Vyas} \\
\indent \textbf{\url{Ashutoshvyas291gmail.com}} \\
\indent Mobile No.: \textbf{9149117784} \ \\
\indent \textbf{\url{https://github.com/Ash20vyas}}\\
\indent \textbf{\url{https://www.linkedin.com/in/ashutoshvyas291}}\\

\resheading{\textbf{EDUCATION} }\\[\lsep]
\\
%\begin{table}[ht!]
%\begin{center}
\indent \rule{7.34in}{0.4pt}\\
\indent \begin{tabular}{ l @{\hskip 0.17in} l @{\hskip 0.17in} l @{\hskip 0.17in} l @{\hskip 0.17in} }
\noindent \textbf{Year} & \textbf{Degree/Exam} & \textbf{Institute} & \textbf{GPA/Marks(\%)}\\
2019 - 2023 & $B.Tech$ $CSE$ with Specialization in $ML$ $\&$ $AI$ & Graphic Era (Deemed to be University) & 9.278/10 \\
2019 & $12^{th}$,\ I.S.C. & St.Joseph's Academy,\ Dehradun & 88.75 \% \\
2017 & $10^{th}$,\ I.C.S.E. & Carmel School,\ Chamba & 90.80 \%\\

\end{tabular}
\indent \rule{7.34in}{0.4pt}
%\end{center}
%\end{table}


\resheading{\textbf{EXPERIENCE} }\\[\lsep]
\begin{itemize}[itemsep=0.01mm, parsep=0.1pt]
\item \textbf{Goldman Sachs |} Summer Analyst \textit{(Jun'22 - Jul'22)}\\[\lsep]
\begin{itemize}[itemsep=0.1mm]
\item Worked on the back-end side of a reconciliation system
\item Implemented a message consumer and handler in JAVA as a part of ISO 20022 adoption programme.
\item Utilised JMS and IBM MQ.
\end{itemize}
\item \textbf{Samsung |} PRISM Research Intern \textit{(Jul'21 - Mar'22)}\\[\lsep]
\begin{itemize}[itemsep=0.01mm]
\item Led a team of 4 members.
\item Built a real-time 5G radio environment monitoring application.
\end{itemize}
\item \textbf{The Sparks Foundation |} Data Science and Business Analyst Intern \textit{(Sep'21 - Oct'21)}\\[\lsep]
\begin{itemize}[itemsep=0.01mm]
\item Developed a hybrid model for stock price/performance prediction.
\item Received \href{https://truecertificates.com/verified/V5FZSXAR8E}{\textbf{The Golden Hand}} for excellent performance.
\end{itemize}
\item \textbf{IEEE |}  Summer Intern \textit{(Jun'21 - Jul'21)}\\[\lsep]
\begin{itemize}[itemsep=0.01mm]
\item Worked on a research project on an AI-based Architecture of an IOT-based flood control system under the guidance of \textbf{Mr. Himanshu Rai Goyal}.
\end{itemize}
\end{itemize}

\resheading{\textbf{PROJECTS} }\\[\lsep]
\begin{itemize}[itemsep=0.01mm, parsep=0.1pt]

\item \textbf{GEU Bus Finder} (Feb'22): \\[\lsep]
\begin{itemize}[itemsep=0.01mm, parsep=2pt]
\item Built a cross-platform application for my university along with my peer to track university buses and display all their information to students in real-time under the guidance of \textbf{Dr. Sachin Sharma}.
\item Designed algorithms, implemented cloud databases, and managed various API services.
\end{itemize}

\item \textbf{Stock Market Prediction Model} (Sep'21): \\[\lsep]
\begin{itemize}[itemsep=0.01mm, parsep=2pt]
\item Created a hybrid model for stock price/performance prediction on 20 years of stock and news data.
\item Applied numerical analysis on historical \textbf{BSE SENSEX} stock price and sentimental analysis on news headlines from Times of India. 
\item Attained an impressive \textbf{R2 Score} of \textbf{0.97}.
\item Link: \href{https://github.com/Ash20vyas/TSF-Intern-Tasks/tree/main/%232%20-%20Stock%20Market%20Prediction%20using%20Numerical%20and%20Textual%20Analysis} {\textit{Stock Market Prediction using Numerical and Textual Analysis}}
\end{itemize}

\item \textbf{Mall Customer Segmentation} (Aug'20): \\[\lsep]\begin{itemize}[itemsep=0.01mm, parsep=0.01pt]
\item Formulated a segmentation model from scratch using NumPy arrays that follow the principle of \textbf{Agglomerative Hierarchical Clustering} to cluster a dataset on mall customers. 
\item Achieved a \textbf{Silhouette Score} of \textbf{0.53} for clustering the dataset into seven classes.
\item Link: \href{https://github.com/Ash20vyas/Mall-Customer-Segmentation} {\textit{Mall-Customer-Segmentation}}
\end{itemize}

\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}[itemsep=0.1mm, parsep=0pt]
\item \noindent \textbf{Languages:} \textbf{Python} (Advanced), \textbf{JAVA}, \textbf{C++}, \textbf{C}, \textbf{DART},  \textbf{SQL}
\item \noindent\textbf{Tools and Frameworks:} Azure Machine Learning Studio, Flutter, Tensorflow, scikit-learn, OpenCV.
\end{itemize}

\resheading{\textbf{SCHOLASTIC \& CO-SCHOLASTIC ACHIEVEMENTS} }\\[\lsep]
\begin{itemize}[itemsep=0.01mm, parsep=2pt]
\item \noindent Got Certified in TensorFlow Developer Certificate
\item \noindent Microsoft Certified: Azure AI Fundamentals
\item \noindent Completed Summer Internship at IEEE with excellent grade.
\item \noindent Organized an inter-university chess competition with 500+ participants
\item \noindent Secured Ist rank in a coding competition by GEU ACM Student Chapter in Ist year B.TECH
\end{itemize}
\end{document}